A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-09 paper.tex
placement of figures 11, 12
fixing spelling in 5.1

Overall, the results show that the conventional tests are more sensitive
than the visual test. The conventional tests do have higher power for
the patterns they are designed to detect, and generaly unable to detect
other patterns. The visual test doesn't require specifiying the pattern
ahead of time, relying purely on whether the observed residual plot is
detectably different from ``good'' residual plots. They will perform
equally well regardless of the type of model defect. This aligns with
the advice of experts on residual analysis, who consider residual plot
analysis to be an indispensable tool for diagnosing model problems. What
we gain from using a visual test for this purpose is the removal of
subjective argument about whether a pattern is visible or not. The
lineup protocol provides the calibration of detecting patterns, that if
the pattern in the data plot cannot be distinguished from patterns in
good residual plots, then no discernible problem with the model exists.

>>>>

Overall, the results show that the conventional tests are more sensitive
than the visual test. The conventional tests do have higher power for
the patterns they are designed to detect, and are generally unable to
detect other patterns. The visual test doesn't require specifying the
pattern ahead of time, relying purely on whether the observed residual
plot is detectably different from ``good'' residual plots. They will
perform equally well regardless of the type of model defect. This aligns
with the advice of experts on residual analysis, who consider residual
plot analysis to be an indispensable tool for diagnosing model problems.
What we gain from using a visual test for this purpose is the removal of
subjective argument about whether a pattern is visible or not. The
lineup protocol provides the calibration of detecting patterns, that if
the pattern in the data plot cannot be distinguished from patterns in
good residual plots, then no discernible problem with the model exists.
